%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Engineer} % Job title
    {Exception Technologies, LLC} % Organization
    {Syracuse, NY} % Location
    {September 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Developed continuous integration system for a proprietary symbolic execution platform using Gitlab CI and Cucumber.}
      	\item {Developed new plugins for VM introspection for the symbolic execution platform using C++.}
      	\item {Debugged and troubleshot the symbolic execution platform for various test cases and execution environments.}
      	\item {Researched virtual hard disk formats for a project involving the qemu virtualization platform.}
      	\item {Researched the current state of the art in uncertainty quantification.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior CIP Analyst} % Job title
    {National Grid} % Organization
    {Syracuse, NY} % Location
    {March 2015 - September 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a custom Linux environment for use on substation computers to run fault collection and analysis.}
        \item {Wrote Python scripts to monitor the health and operation of substation computers.}
        \item {Worked with the developers of the Wavewin software to create extensions for monitoring substation equipment and retrieving data from it.}
        \item {Developed configurations for many different types of network hardware from RuggedCom (Siemens), Schweitzer and GarrettCom.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Associate Engineer} % Job title
    {Assured Information Security} % Organization
    {Rome, NY} % Location
    {November 2012 - March 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Debugged and tested the SecureView multi-domain desktop virtualization software written primarily in C++.}
        \item {Maintained the build system for SecureView and developed the build/release process.}
        \item {Debugged the Javascript front-end for SecureView and oversaw the team of subcontractors tasked with fixing the issues.}
        \item {Integrated the Apache Traffic Server with custom software designed to offload analysis of web traffic to a highly optimized parallel computing application implemented in OpenCL.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Systems Integration and Test Engineer} % Job title
    {Lockheed Martin} % Organization
    {Syracuse, NY} % Location
    {May 2009 - November 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed formal software and hardware testing of radar and sonar systems.}
        \item {Developed an in-depth knowledge of radar and sonar systems in order to effectively troubleshoot and isolate problems.}
        \item {Completed various network design and configuration tasks on RuggedCom, Cisco and 3Com hardware.}
        \item {Configured several Linux/UNIX variants on many different types of hardware, built and debugged Linux kernels and drivers.}
        \item {Designed and implemented a Remote Installation Procedure for the system using various Linux tools and bash scripts to automate its installation aboard ships.}
        \item {Traveled frequently to various military installations to troubleshoot system problems and support field testing.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
